Expected Option Returns and the risk-free Rate in Crypto Asset Markets

### 2024-01-14 written/paper.tex
second compressed table
third compressed table
added pvalue table

\title{Pricing Kernels and Risk Premia implied in Bitcoin Options}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{7 January 2024}

@@

\section{Introduction}

@@

This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option positions in the early 2000s.

@@

@@

As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.

@@

\begin{table}[ht]
\begin{tabular}{llrrrrrrr}
\hline
\textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\hline
\hline
\# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
\# Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
\# Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
\# OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
\# Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
\# BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
\# Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
\# Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
\# Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
\# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30                     
\end{tabular}
\end{table}

@@

\begin{tabular}{llrrrrrrr}

@@

@@

@@

@@

>>>>

\title{Expected Option Returns and the risk-free Rate in Crypto Asset Markets}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{7 January 2024}

@@

\section{Introduction}
Despite the ongoing attention that crypto assets receive and despite their ongoing integration into traditional markets, whereas the last example would be the SEC's approval of a range of Bitcoin Spot ETFs, fundamental questions about crypto asset markets remain unclear:
How efficient are crypto asset markets relative to established, traditional markets such as equities? 
Does a risk-free rate exist and if yes, how does it relate to the risk-free rate in established markets? Are derivatives, written on crypto assets, fairly priced or at least fairly priced relative to other derivatives? What do we know about the risk-return characteristics of crypto assets?
We assess these fundamental questions and find that the methods required to conduct our analysis have been out in the open for long; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s. 
The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway and Bakshi et al in XZY year.

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., severe overpricings of at-the-money options. The effect holds after compensating for market crash insurance and transaction cost. 
We assess the deadeweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.

Evidence for leverage effect?

We constructs and evaluate the empirical performance of option portfolios, written on crypto assets such as Bitcoin and Ether, to allow model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.

What evidence or contradictions can we find?
The precise and bespoke tailoring of risk-return characteristics through the use of options allows promising insights into the risk-return characteristics of crypto assets, such as Bitcoin and Ether.

From our point of view, the primary question leading such research is the question of market efficiency.

Due to the youth of the crypto asset option markets, the primary question foregoing such research is that of the efficiency of named market. Do the laws that govern equity option markets also apply to crypto asset option markets? Can we find empirical evidence or contradictions?

- Is there a risk-free rate in crypto markets?
- How efficient is the crypto (option) market compared to equity option markets?

@@

This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option portfolios in the early 2000s.

@@

\section{Methodology}

We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
The exchange started operations in July 2017. 
Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates since (approx.) July 2019.

- table of amount of transactions per group
- plot: amount of transactions over time per group (crypto)

@@

As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
Open Interest for Ether Perpetual Futurews contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.

@@

\begin{table}[ht]
\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
\hline
\textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\hline
\hline
\# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
\# Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
\# Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
\# OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
\# Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
\# BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
\# Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
\# Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
\# Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
\# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30                     
\end{tabular}}
\end{table}

@@

\begin{table}[ht]
\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
\hline

@@

\hline
\hline

@@

\end{tabular}}

@@

Solve for interest rates from

\begin{equation}
F_t = e^{r \tau} S_t
\end{equation}

@@

We conduct a left-sided t-test to test for a population mean of zero. Values are rounded to 4 digits.
\begin{tabular}{lllll}
     & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\
0.7  & 0.6088         & 0.5854          & 0.5845                 & 0.6078                  \\
0.71 & 0.7993         & 0.7769          & 0.7762                 & 0.7987                  \\
0.72 & 0.9943         & 0.9925          & 0.9925                 & 0.9943                  \\
0.73 & 0.9348         & 0.9222          & 0.9222                 & 0.9348                  \\
0.74 & 0.9997         & 0.9996          & 0.9996                 & 0.9997                  \\
0.75 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.76 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.77 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.78 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.79 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.8  & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.81 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.82 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.83 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.84 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.85 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.86 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.87 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.88 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.89 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.9  & 1.0            & 1.0             & 1.0                    & 1.0                     \\
0.91 & 1.0            & 0.9998          & 0.9998                 & 1.0                     \\
0.92 & 1.0            & 0.9968          & 0.9968                 & 1.0                     \\
0.93 & 0.9984         & 0.9437          & 0.9437                 & 0.9984                  \\
0.94 & 0.9669         & 0.6277          & 0.6277                 & 0.9669                  \\
0.95 & 0.8817         & 0.3093          & 0.3093                 & 0.8817                  \\
0.96 & 0.3229         & 0.0129          & 0.0129                 & 0.3229                  \\
0.97 & 0.2143         & 0.0047          & 0.0047                 & 0.2143                  \\
0.98 & 0.0082         & 0.0             & 0.0                    & 0.0082                  \\
0.99 & 0.0002         & 0.0             & 0.0                    & 0.0002                  \\
1.0  & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.01 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.02 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.03 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.04 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.05 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.06 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.07 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.08 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.09 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.1  & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.11 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.12 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.13 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
1.14 & 0.0172         & 0.0106          & 0.0106                 & 0.0172                  \\
1.15 & 0.0484         & 0.0347          & 0.0347                 & 0.0484                  \\
1.16 & 0.0563         & 0.0421          & 0.0421                 & 0.0564                  \\
1.17 & 0.1889         & 0.1588          & 0.1587                 & 0.1887                  \\
1.18 & 0.8503         & 0.8119          & 0.8115                 & 0.8499                  \\
1.19 & 0.9906         & 0.9861          & 0.9859                 & 0.9905                  \\
1.2  & 0.8888         & 0.8593          & 0.8562                 & 0.8862                  \\
1.21 & 0.9796         & 0.9713          & 0.9701                 & 0.9787                  \\
1.22 & 0.986          & 0.9805          & 0.9793                 & 0.985                   \\
1.23 & 0.9627         & 0.951           & 0.9464                 & 0.959                   \\
1.24 & 0.9969         & 0.9954          & 0.9945                 & 0.9962                  \\
1.25 & 0.9976         & 0.9966          & 0.9957                 & 0.9969                  \\
1.26 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
1.27 & 0.9999         & 0.9999          & 0.9998                 & 0.9999                  \\
1.28 & 0.9996         & 0.9995          & 0.9993                 & 0.9995                  \\
1.29 & 0.9939         & 0.9932          & 0.9919                 & 0.9927                  \\
1.3  & 0.9436         & 0.9403          & 0.9334                 & 0.937                  
